% Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
% LicenseCreative Commons CC BY 4.0
% Job application cover letter. Useful for Instructor/Guest Faculty/ Asst. Professor/ Others. Auto date
% Overleaf Source: https://www.overleaf.com/latex/templates/job-application-cover-letter/jgbntsgkcvvz

% (c) 2022 Labin Ojha <leabstrait@gmail.com> https://github.com/leabstrait


\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Labin}{Ojha}
\email{kontaktlabin@gmail.com}
\phone[mobile]{+44 07463 751853}
\address{London, United Kingdom}


\begin{document}

\recipient{To}{The HR Manager, \\
    Logpoint Nepal, \\
    Lalitpur, Nepal}
\date{\today}
\opening{\textbf{Sub: Application for “Software Engineer (Python)” role at
        Logpoint Nepal with reference advertisement: XXXX/XX, dated 04-03-2022.}}
\closing{Your Sincerly, \vspace{-1em}}


% \enclosure[Enclosed (Marksheets/Certificates)]{
%     \\ 1. SSLC (Admit/MarkSheet/Certificate)
%     \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%     2. Diploma (MarkSheet/Certificate)
%     \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\
%     3. B.Tech (MarkSheet/Certificate)
%     \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%     4. M.Tech (MarkSheet/Certificate)
%     \hspace{2.1em} 8. Caste Certificate \\
% }
\makelettertitle



Respected Sir,
\\
%references such as what and how you got this information
\vspace{1em}
With reference to the subject as cited above, I Labin Ojha, would like to
apply for a “Software Engineer (Python)” role at Logpoint Nepal. I found
the said reference through a job portal site and information provided in
the company official website.\\

%narrate why you want to apply
\vspace{1em}
I am comfortable working with python and it’s Flask framework and SQL
databases to build web applications. The team I worked with previously
used a custom configured VPS to host their applications, yet I have
cursory knowledge of Cloud deployments and some CI/CD as well, with Heroku,
Github Actions.  \\
\vspace{1em}

%add some experiences
I am a graduate with a BSc. in Computer Science from Tribhuvan University
and have previously worked as a full stack software developer with Beta
Analytics Pvt. Ltd. on their in-house project.

%conclusion
\vspace{1em}
I am confident I can learn any new technology on the job. I also have a deep
interest in emerging technologies and the businesses that they enable.
I believe I can provide value to your company and also fuel my personal
growth as a developer in this role available at your company.

\vspace{1em}
I would very much like to discuss the aforementioned opportunity at your
company. To schedule an interview, please call me at \href{tel://+44 07463 751853}{+44 07463 751853}.
Thank you for taking the time to review my resume. I look forward to
talking with you.


\vspace{0.5cm}


\makeletterclosing

\end{document}