\documentclass{article}
\usepackage[margin=1.5in]{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{xifthen}


\renewcommand{\maketitle}{
    \begin{center}
        {\huge\bfseries\theauthor}

        \vspace{.25em}
        Lalitpur, Nepal

        \vspace{.25em}
        +977 9823663223

        \vspace{.25em}
        kontaktlabin@gmail.com

        \vspace{.25em}
        https://github.com/leabstrait



    \end{center}
}

% \titleformat{\section}
% {\huge\bfseries}
% {\thesection}
% {0.5em}
% {- }

\titleformat{\section}
{\huge}
{}
{.25em}
{\bfseries}[\titlerule]

\titleformat{\subsection}
{\Large\bfseries}
{$\hspace{.25in}\bullet$}
{0.5em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[--]

\titlespacing{\subsubsection}{3em}{.25em}{1em}

% Making the \entry command
\newcommand{\entry}[4]{
    \ifthenelse{\isempty{#3}}
    {\slimentry{#1}{#2}}{

        \begin{minipage}[t]{.15\linewidth}
            \hfill \textsc{#1}
        \end{minipage}
        \hfill\vline\hfill
        \begin{minipage}[t]{.80\linewidth}
            {\bf#2}\\\textit{#3} \footnotesize{#4}
        \end{minipage}\\
        \vspace{.2cm}
    }}

\newcommand{\slimentry}[2]{

    \begin{minipage}[t]{.15\linewidth}
        \hfill \textsc{#1}
    \end{minipage}
    \hfill\vline\hfill
    \begin{minipage}[t]{.80\linewidth}
        #2
    \end{minipage}\\
    \vspace{.25cm}
}% end \entry command definition

\title{R\'esum\'e}
\author{Labin Ojha}

\begin{document}
\maketitle


\section{Professional Service}

\entry{Dec 2021 - present}
{Pi Tech Info Pvt. Ltd. - Software Engineer}
{Kathmandu, Nepal}
{
    Full-Stack Developer and acting team lead for their product called ‘Chukul’ which offers
    fundamental analysis and technical analysis of stocks as a service.
    Worked with Django, VueJS, TradingView
}

\entry{Feb 2020 - Sep 2021}
{Beta Analytics Pvt. Ltd. - Software Developer}
{Kathmandu, Nepal}
{
    Full-Stack Developer on their in-house data entry and reporting system.
    Full-Stack Developer on a web application framework for stockbrokers.
    Developed a browser extension for automation of form filling via fetch from a remote resource
}

\entry{Jan 2020 - Feb 2020}
{Sudreeshya IT Training Academy - Python Instructor}
{Kathmandu, Nepal}
{
    Delivered a course in Python programming to 3rd-year college students
}

\entry{Feb 2018 - Dec 2019}
{Innovative Engineering and Construction Technologies Pvt. Ltd. - Information Systems Officer}
{Kathmandu, Nepal}
{
    \begin{itemize}
        \item Managed and oversaw the development of their websites and mobile apps
        \item Maintained and Monitored the organisation’s ERP software(Bitrix24) and other computing and network equipment
        \item Tested and evaluated new technologies
        \item Proposed hardware/software solutions to accomplish the company's business objectives
        \item Documented, Reported findings and observations for Business Process Optimization.
    \end{itemize}
}


\entry{Sep 2017 - Dec 2017}
{Bajra Technologies Pvt. Ltd. - Software Development Intern}
{Kathmandu, Nepal}
{
    Built a backend module in Golang for one of their in-house project named ‘Sitehawk’ which
    is a website monitoring service
}

\entry{2015 - 2016}
{CSIT Association of Nepal - Executive Member}
{Kathmandu, Nepal}
{
    Participated in committee meetings and assisted in events held by the organization
}

\section{Tools and Technologies}

\begin{itemize}
    \item Programming Languages: Python, JavaScript
    \item Version Control and Source Code Management: Git, GitHub
    \item System Infrastructure: Linux, Docker
    \item Productivity: MS Office, Jira, Bitrix24
\end{itemize}

\section{Education}

\entry {2014 - 2018}
{Tribhuvan University - BSc. Computer Science and Information Technology}
{Lalitpur, Nepal}
{Took courses in Computer Programming, Data Structures, Algorithms,
    System Analysis and Design, Computation Theory, Artificial Intelligence,
    Statistics and Machine Learning
    The final year project was an android application for Algorithm Visualization.
}

\entry {2010 - 2012}
{Capital Higher Secondary School - High School Certificate}
{Kathmandu, Nepal}
{Studied Physics, Mathematics, Computer Science
    Participated in Science Exhibitions
    Founding Member of an IT Club
}

\entry {- 2010}
{Lalitpur Secondary Boarding School - School Leaving Certificate}
{Lalitpur, Nepal}
{Participated in Science Exhibitions and other extracurriculars}

\section{Participations and Activities}

\begin{itemize}
    \item Conducted a business case study of Sastodeal on “Improving customer retention rate in the eCommerce marketplace” at Glocal Skill Week 2021 (29 March 2021)
    \item Attended ThreatCon 2019, a local-level cybersecurity conference. Participated in CTF(Capture The Flag) competition at the event with a team (31 Aug 2019)
    \item Participated in Youth Leadership Forum training organized by International Community Development Foundation (ICDF) and American Embassy. Key themes of the training were: 21st Century Leadership, Self-Exploration, Resource Exploration, and Enterprise Building (5 - 7 June 2019)
    \item Participated in Nepal Internet Governance Forum 2018, voiced opinions, and carried out discussions regarding Internet usage, safety, and policy (2-3 Nov 2018)
    \item Participated in Open Data Hackathon - 2015 with a team. Presented a prototype project called ‘Prakriya’ which offers easy information about administrative processes in Government Offices. I was responsible for extracting data from pdf files. (7 Mar 2015)
    \item Volunteered at Yantra 1.0 - National Robotics Competition organized by Robotics Association of Nepal (20-21 July 2012)
\end{itemize}


\end{document}