% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
% (c) 2022 Labin Ojha <leabstrait@gmail.com> https://github.com/leabstrait
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{hyperref}
\robustify\cftdotfill


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands

\newcommand{\cvheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\cvsubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\cvitem}[1]{\item #1 \vspace{-2pt}}

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
      \textbf{\Large Labin Ojha} & \href{tel://+44 07463 751853}{+44 07463 751853} \\
      Software Developer and Team Lead at PitechInfo & \href{mailto:kontaktlabin@gmail.com}{kontaktlabin@gmail.com} \\
      \href{https://github.com/leabstrait}{\texttt{https://github.com/leabstrait}}  & London, United Kingdom \\
      &\tiny{Last Updated: \textbf{\today}} \href{https://cv.labinojha.com.np/cv-labin-ojha.pdf}{Download}
\end{tabular*}
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

      \item
            \cvsubheading{Pi Tech Info Pvt. Ltd.}{Kathmandu, Nepal}{Software Team Lead}{December 2021 - September 2022}
            \begin{itemize}
                  \cvitem{Full-Stack Developer and acting team lead for their product called \href{https://chukul.com}{'Chukul'} which offers fundamental analysis and technical analysis of stocks as a service.}
                  \cvitem{Worked with Django, Vue.js, Quasar UI, TradingView}
                  \cvitem{Launched the product in a short timeframe and helped the company breakeven after about 4 months of launch.}
            \end{itemize}

      \item
            \cvsubheading{Beta Analytics Pvt. Ltd.}{Kathmandu, Nepal}{Software Developer}{Feb 2020 - September 2021}
            \begin{itemize}
                  \cvitem{Full-Stack Developer on their in-house data entry and reporting system.}
                  \cvitem{Full-Stack Developer on a web application framework for stockbrokers. The framework allowed multiple revenue streams while being based on a single system.
                        The sites had features like:
                        managing downloadable content, creating and updating notices and blog posts, and KYC forms}
                  \cvitem{List of websites using the framework}:
                  \begin{itemize}
                        \item \href{https://www.premiersecurities.com.np/}{'Premier Securities'}
                        \item \href{https://www.swetasecurities.com/}{'Sweta Securities'}
                        \item \href{https://mallastock.com/}{'Malla \& Malla Stockbroking Co.'}
                  \end{itemize}
                  \cvitem{Developed a browser extension to automate filling up forms.}
            \end{itemize}

      \item
            \cvsubheading{Sudreeshya IT Training Academy}{Kathmandu, Nepal}{Python Instructor}{Jan 2020 - Feb 2020}
            \begin{itemize}
                  \cvitem{Delivered a \href{https://github.com/leabstrait/basic-python-class}{course} in Python programming to 3rd-year college students.}
                  \cvitem{Each student was assigned an end-of-course project and they demonstrated considerable understanding of the concepts. Many of them are employed now in good companies.}
            \end{itemize}

      \item
            \cvsubheading{Innovative Engineering and Construction Technologies Pvt. Ltd.}{Kathmandu, Nepal}{Information Systems Officer}{Feb 2018  - Dec 2019}
            \begin{itemize}
                  \cvitem{Managed and oversaw the development of their website - \href{https://meroghar.com}{Meroghar Website} and mobile app}
                  \cvitem{Maintained and Monitored the organisation’s ERP software(Bitrix24)}
                  \cvitem{Setup, Operation and Troubleshooting of computing and network equipment like Routers and Switches, CCTV, Access Control and Attendance Systems, IVR}
                  \cvitem{Tested and evaluated new tools and technologies. Proposed hardware/software solutions to accomplish the company's business objectives}
                  \cvitem{Negotiated pricing and fees with various software providers and equipment vendors to cut down operation costs of the organization.}
                  \cvitem{Documented \& Reported findings and observations for Business Process Optimization.}
            \end{itemize}
            \cvsubheading{Bajra Technologies Pvt. Ltd.}{Kathmandu, Nepal}{Software Development Intern}{Sep 2017 - Dec 2017}
            \begin{itemize}
                  \cvitem{Built a backend module in Golang for one of their in-house project named \href{https://sitehawk.io}{‘Sitehawk’} which is a website monitoring service}
                  \cvitem{The module utilized Bing Search API to determine rankings of our client's websites which was quite useful and appreciated.}
            \end{itemize}

      \item
            \cvsubheading{CSIT Association of Nepal}{Kathmandu, Nepal}{Executive Member}{2015 - 2016}
            \begin{itemize}
                  \cvitem{Built and wrote content for their very first website - \href{https://csitan.org.np/}{CSITAN}}
                  \cvitem{Participated in committee meetings.}
                  \cvitem{Assisted in events held by the organisation which included sponsored Training Programs, Tech Community Meetups and Panel Discussions pertaining to the IT sector in Nepal.}
                  \cvitem{During my tenure, we also expanded our organization to include students and colleges of Computer Science throughout Nepal by establishing regional units of our organization.}
            \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

      \item {\bf Computer Science:} Data Structures and Algorithms, Machine Learning, Artificial Intelligence, Linear Algebra,

      \item {\bf Programming:} Python (preferred), Javascript, \LaTeX

      \item {\bf Technologies:}
            \begin{itemize}
                  \item {\bf Web Frameworks}: Flask, Django
                  \item {\bf JS Frameworks}: Vue.js, TradingView
                  \item {\bf Databases:} PostgreSQL
                  \item {\bf Systems:} Linux, Docker
                  \item {\bf DevTools:} git, tmux, Makefile
            \end{itemize}

      \item {\bf Teaching:} I've given several classes and tutorials to students and interested audiences.

      \item Discovering and implementing new ideas. Give me an API and a problem and I will figure it out.

      \item Background in Math, Computer Science, allows me break down problems and find solutions.

      \item I can learn and adapt to a new discipline, area or environment and get results quickly.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
      \item
            \cvsubheading{Tribhuvan University}{Kathmandu, Nepal}{BSc. Computer Science and Information Technology}{2014 - 2018}
            \begin{itemize}
                  \cvitem{Took courses in Computer Programming, Data Structures \& Algorithms, System Analysis and Design, Computation Theory, Artificial Intelligence, Statistics and Machine Learning}
                  \cvitem{The final year project was an android application for Algorithm Visualization.}
            \end{itemize}

      \item
            \cvsubheading{Capital Higher Secondary School}{Kathmandu, Nepal}{High School Certificate}{2010 - 2012}
            \begin{itemize}
                  \cvitem{Studied Physics, Mathematics, Computer Science}
                  \cvitem{Participated in Annual Science Exhibitions. Notable exhibit - 'High Voltage Show' which included a Tesla Coil Disco Ball, Jacob's Ladder, a Makeshift Oscillator along with a display of various High Voltage Components used in machines around us.}
                  \cvitem{Founding Member of an IT Club}
            \end{itemize}

      \item
            \cvsubheading{Lalitpur Secondary Boarding School}{Lalitpur, Nepal}{School Leaving Certificate}{2010}
            \begin{itemize}
                  \cvitem{Participated in Annual Science Exhibitions. Notable exhibit - A remote-controlled robot that drilled and extracted fluids from underground.}
            \end{itemize}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvheading{Participation in Workshops and Conferences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

      \item
            \cvsubheading{THREAT CON 2019}{Kathmandu, Nepal}{ThreatNix Pvt. Ltd.}{31 Aug 2019}
            \begin{itemize}
                  \cvitem{A local-level cybersecurity conference.}
                  \cvitem{Participated in CTF(Capture The Flag) competition at the event with a team }
            \end{itemize}

      \item
            \cvsubheading{Youth Leadership Forum training}{Lalitpur, Nepal}{International Community Development Foundation (ICDF), American Embassy}{5 - 7 June 2019}
            \begin{itemize}
                  \cvitem{Key themes of the training were: 21st Century Leadership, Self-Exploration, Resource Exploration, and Enterprise Building}
            \end{itemize}

      \item
            \cvsubheading{Nepal Internet Governance Forum 2018}{Lalitpur, Nepal}{Internet Governance Forum, Nepal Chapter}{2-3 Nov 2018}
            \begin{itemize}
                  \cvitem{Carried out discussions regarding Internet usage, safety, and policy}
            \end{itemize}

      \item
            \cvsubheading{Open Data Hackathon - 2015}{Kathmandu, Nepal}{Open Data Nepal}{7 March 2015}
            \begin{itemize}
                  \cvitem{With a team, presented a prototype project called ‘Prakriya’ which offers easy information about administrative processes in Government Offices. I was responsible for extracting data from pdf files.}
            \end{itemize}

      \item
            \cvsubheading{Yantra 1.0 - National Robotics Competition}{Kathmandu, Nepal}{Robotics Association of Nepal}{20-21 July 2012}
            \begin{itemize}
                  \cvitem{Volunteered}
            \end{itemize}
\end{itemize}

\pagebreak

\end{document}
